---
title: "Posts about R"
date: "2022-10-05"
---

## Writing Functions in R

A function is a block of code which only runs when it is called.

You can pass data, known as parameters, into a function.

A function can return data as a result.

Creating a Function To create a function, use the function() keyword:

```{r}
my_function <- function() { # create a function with the name my_function
  print("Hello World!")
}

my_function
```

Link: [W3 Schools](https://www.w3schools.com/r/r_functions.asp)

## Using Pie Chart in R

Pie Charts A pie chart is a circular graphical view of data.

Use the pie() function to draw pie charts:

```{r}
# Create a vector of pies
x <- c(10,20,30,40)

# Display the pie chart
pie(x)
```

Link: [W3 Schools](https://www.w3schools.com/r/r_graph_pie.asp)

## Find data type of an object in R

To find the data type of an object you have to use **class()** function. The syntax for doing that is you need to pass the object as an argument to the function **class()** to find the data type of an object.

```{r}
# A simple R program
# to find data type of an object
 
# Logical
print(class(TRUE))
 
# Integer
print(class(3L))
 
# Numeric
print(class(10.5))
 
# Complex
print(class(1+2i))
 
# Character
print(class("12-04-2020"))
```

Link: [Geeksforgeeks](https://www.geeksforgeeks.org/r-data-types/?ref=lbp)
